---
title: "01b_BRMS"
author: "Wade VanderWright"
date: '2022-03-24'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#01_b -- BRMS Models for Ch. 1
## VanderWright, WJ
## May 27, 2022
## Updated: November 1, 2022

## Model 1 - GSH ~ CFAR

```{r}
# get uninformative priors
brms_1_prior <- get_prior(LogMeanGSH_centered ~ LogCFAR_centered + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    data2 = list(B = B),
                    family = gaussian())

# run 
brms_1 <- brm(LogMeanGSH_centered ~ LogCFAR_centered + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    data2 = list(B = B),
                    family = gaussian(),
                    prior = brms_1_prior,
                    warmup = 1000, iter = 5000,
                    cores = 4
                    )

summary(brms_1)
```

```{r}
#visual check
plot(conditional_effects(brms_1), points = TRUE)

```

```{r}
#visual check 2
plot(brms_1, N=2, ask = F)

```


```{r}
#lamda estimate
hyp <- "sd_Binomial__Intercept^2 / (sd_Binomial__Intercept^2 + sigma^2) = 0"
(hyp <- hypothesis(brms_1, hyp, class = NULL))
```


```{r}
plot(hyp)
```

## Model 2 - GSH ~ Max Size
```{r}
brms_2_prior <- get_prior(LogMeanGSH_centered ~ LogMaxSize_centered + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    data2 = list(B = B),
                    family = gaussian())

brms_2 <- brm(LogMeanGSH_centered ~ LogMaxSize_centered + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    data2 = list(B = B),
                    family = gaussian(),
                    prior = brms_2_prior,
                    warmup = 1000, iter = 5000,
                    cores = 4
                    )

summary(brms_2)

```


```{r}
plot(conditional_effects(brms_2), points = TRUE) #hit enter in the console

```

```{r}
plot(brms_2, N=2, ask = F)

```


```{r}
#lamda estimate
hyp <- "sd_Binomial__Intercept^2 / (sd_Binomial__Intercept^2 + sigma^2) = 0"
(hyp <- hypothesis(brms_2, hyp, class = NULL))
```
```{r}
plot(hyp)
```


## Model 3 - GSH ~ Median Depth 
```{r}
brms_3_prior <- get_prior(LogMeanGSH_centered ~ LogDepthMedian_centered + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    family = gaussian(),
                    data2 = list(B = B))

#run time was about 30 minutes the first time
brms_3 <- brm(LogMeanGSH_centered ~ LogDepthMedian_centered + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    family = gaussian(),
                    data2 = list(B = B),
                    prior = brms_3_prior,
                    cores = 4,
                    warmup = 1000, iter = 5000)

summary(brms_3)


```


```{r}
plot(conditional_effects(brms_3), points = TRUE)

```

```{r}
plot(brms_3, N=2, ask = F)

```


```{r}
#lamda estimate
hyp <- "sd_Binomial__Intercept^2 / (sd_Binomial__Intercept^2 + sigma^2) = 0"
(hyp <- hypothesis(brms_3, hyp, class = NULL))
```

```{r}
plot(hyp)
```


## Model 4 - CFAR ~ GSH + MaxSize + Median Depth
```{r}
brms_4_prior <- get_prior(LogMeanGSH_centered ~ LogCFAR_centered + LogMaxSize_centered + LogDepthMedian_centered + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    family = gaussian(),
                    data2 = list(B = B))

brms_4 <- brm(LogMeanGSH_centered ~ LogCFAR_centered + LogMaxSize_centered + LogDepthMedian_centered + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    family = gaussian(),
                    data2 = list(B = B),
                    prior = brms_4_prior,
                    chains = 4, cores = 4,
                    warmup = 1000, iter = 5000)

summary(brms_4)
```

```{r}
conditions <- data.frame(LogDepthMedian_centered = c(-1, 0, 1))
plot(conditional_effects(brms_4, effects = "LogCFAR_centered:LogDepthMedian_centered",  spaghetti = FALSE, ndraws = 1000), points = TRUE, probs = 0)
```

```{r}
#lamda estimate
hyp <- "sd_Binomial__Intercept^2 / (sd_Binomial__Intercept^2 + sigma^2) = 0"
(hyp <- hypothesis(brms_4, hyp, class = NULL))
plot(hyp)
```


```{r}
pp_check(brms_4)
```

```{r}
plot(conditional_effects(brms_4), points = TRUE, ask = FALSE)
```
```{r}
plot(brms_4, N = 2, ask = FALSE)
```



## Model 5 - CFAR ~ GSH + MaxSize + Median Depth + Endothermy
```{r}
brms_5_prior <- get_prior(LogMeanGSH_centered ~ LogCFAR_centered + LogMaxSize_centered + LogDepthMedian_centered + endothermy + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    family = gaussian(),
                    data2 = list(B = B))

brms_5 <- brm(LogMeanGSH_centered ~ LogCFAR_centered + LogMaxSize_centered + LogDepthMedian_centered + endothermy + (1|gr(Binomial, cov = B)),
                    data = GSH_df_full,
                    family = gaussian(),
                    data2 = list(B = B),
                    prior = brms_4_prior,
                    chains = 4, cores = 4,
                    warmup = 1000, iter = 5000)




summary(brms_5)
```
```{r}
plot(conditional_effects(brms_5), points = TRUE, ask = FALSE)

```

```{r}
plot(brms_5, N=2, ask = FALSE)
```



```{r}
plot(x = GSH_df_full$endothermy, y = exp(GSH_df_full$LogMeanGSH))
```

```{r}
#lamda estimate
hyp <- "sd_Binomial__Intercept^2 / (sd_Binomial__Intercept^2 + sigma^2) = 0"
(hyp <- hypothesis(brms_5, hyp, class = NULL))
plot(hyp)
```



## R2 vals
```{r}
bayes_R2(brms_1)
```

```{r}
bayes_R2(brms_2)
```

```{r}
bayes_R2(brms_3)
```

```{r}
bayes_R2(brms_4)
```

```{r}
bayes_R2(brms_5)
```



## pp checks

```{r}
pp_check(brms_1, ndraws = 150)
```

```{r}
pp_check(brms_2, ndraws = 150)
```

```{r}
pp_check(brms_3, ndraws = 150)
```

```{r}
pp_check(brms_4, ndraws = 150)
```





##LOO comapre (quick and dirty version)

```{r}
fit1_loo <- loo(brms_1)
fit2_loo <- loo(brms_2)
fit3_loo <- loo(brms_3)
fit4_loo <- loo(brms_4)
fit5_loo <- loo(brms_5)


brms_loo_phylo_list <- list(fit1_loo, fit2_loo, fit3_loo, fit4_loo, fit5_loo)
brms_loo_phylo <- loo_compare(brms_loo_phylo_list)
loo_model_weights(brms_loo_phylo_list)

LOO_Table <- data.frame(round(brms_loo_phylo, 2))

write.csv(LOO_Table, file = here("./Data/Output/LOO_Table2.csv"), row.names = T)

brms_loo_phylo
```

## Summary of models
```{r}
tbl1_title <- data.frame("Model 1 - Activity",NA,NA,NA)
names(tbl1_title) <- names(Table_1)
Table_1 <- data.frame(round(fixef(brms_1, summary = TRUE), 2))
tbl2_title <- data.frame("Model 2 - Size",NA,NA,NA)
names(tbl2_title) <- names(Table_1)
Table_2 <- data.frame(round(fixef(brms_2, summary = TRUE), 2))
tbl3_title <- data.frame("Model 3 - Depth",NA,NA,NA)
names(tbl3_title) <- names(Table_1)
Table_3 <- data.frame(round(fixef(brms_3, summary = TRUE), 2))
tbl4_title <- data.frame("Model 4 - Ecological lifestyle",NA,NA,NA)
names(tbl4_title) <- names(Table_1)
Table_4 <- data.frame(round(fixef(brms_4, summary = TRUE), 2))


Table_5 <- rbind(tbl1_title,Table_1,
                 tbl2_title,Table_2,
                 tbl3_title,Table_3,
                 tbl4_title,Table_4)

write.csv(Table_5, file = here("./Data/Output/Model_summaries_231007.csv"))
Table_5
```

### Back transform intercepts and units of change
#### Model 1 - CFAR
```{r}
#back transform intercept - 0.44
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.44) + mean(GSH_df_full$LogMeanGSH, na.rm = T)) *100),2)

round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.44) + mean(GSH_df_full$LogMeanGSH, na.rm = T) + (sd(GSH_df_full$LogMeanGSH, na.rm = T))) *100),2)



#when x is 0
round(mean(GSH_df_full$LogCFAR, na.rm = T),2)
exp(mean(GSH_df_full$LogCFAR, na.rm = T) + (sd(GSH_df_full$LogCFAR, na.rm = T)*0.37)) - exp(mean(GSH_df_full$LogCFAR, na.rm = TRUE))

#BCI - -0.1 , 0.98
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*-0.09) + mean(GSH_df_full$LogMeanGSH, na.rm = T))*100),2)
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.96) + mean(GSH_df_full$LogMeanGSH, na.rm = T))*100),2)

#error - 0.27
round((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.27) + mean(GSH_df_full$LogMeanGSH, na.rm = T),2)


```
```{r}
#size of 1SD
round(exp(sd(GSH_df_full$LogCFAR, na.rm = T)),2)
```


#### Model 2 - Size
```{r}
#back transform intercept - 0.29
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.29) + mean(GSH_df_full$LogMeanGSH, na.rm = T))*100),2)

#when x is 0
round(mean(GSH_df_full$LogMaxSize, na.rm = T),2)
round(exp(mean(GSH_df_full$LogMaxSize, na.rm = T)),2)

#BCI - -0.22 , 0.79
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*-0.22) + mean(GSH_df_full$LogMeanGSH, na.rm = T))*100),2)
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.79) + mean(GSH_df_full$LogMeanGSH, na.rm = T))*100),2)

#error - 0.27
round((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.27) + mean(GSH_df_full$LogMeanGSH, na.rm = T),2)
```



#### Model 3 - Depth
```{r}
#size of 1SD
#back transform intercept - 0.38
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*1.24) + mean(GSH_df_full$LogMeanGSH, na.rm = T)) * 100),2)

#when x is 0
round(mean(GSH_df_full$LogDepthMedian, na.rm = T),2)
round(exp(mean(GSH_df_full$LogDepthMedian, na.rm = T)),2)

#BCI - -0.21 , 0.97
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*-0.21) + mean(GSH_df_full$LogMeanGSH, na.rm = T)) * 100),2)
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.97) + mean(GSH_df_full$LogMeanGSH, na.rm = T)) * 100),2)

#error - 0.xx ??
round((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.27) + mean(GSH_df_full$LogMeanGSH, na.rm = T),2)
```

```{r}
#size of 1SD
round(sd(GSH_df_full$LogDepthMedian, na.rm = T),2)
```

#### Model 4 - Ecolife
```{r}
#size of 1SD
#back transform intercept - 0.29
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.37) + mean(GSH_df_full$LogMeanGSH, na.rm = T)) * 100),2)

#when x is 0
round(mean(GSH_df_full$LogCFAR, na.rm = T),2)
round(exp(mean(GSH_df_full$LogCFAR, na.rm = T)),2)

#BCI - -0.16 , 0.74
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*-0.15) + mean(GSH_df_full$LogMeanGSH, na.rm = T)) * 100),2)
round((exp((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.71) + mean(GSH_df_full$LogMeanGSH, na.rm = T)) * 100),2)

#error - 0.xx ??
round((sd(GSH_df_full$LogMeanGSH, na.rm = T)*0.27) + mean(GSH_df_full$LogMeanGSH, na.rm = T),2)
```



### Save the environment
```{r}
save.image(here('./Data/Output/CurrentDataState.RData'))


saveRDS(brms_1, here("Data", "Output", "brms_1.rds"))
saveRDS(brms_2, here("Data", "Output", "brms_2.rds"))
saveRDS(brms_3, here("Data", "Output", "brms_3.rds"))
saveRDS(brms_4, here("Data", "Output", "brms_4.rds"))
saveRDS(brms_5, here("Data", "Output", "brms_5.rds"))
```



