---
title: "Ch. 1 - Model comaprisons"
author: "Wade VanderWright"
date: '2022-02-25'
output: 
  pdf_document:
    fig_height: 5
    fig_width: 7
    df_print: kable
    toc: TRUE
  

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(knitr.table.format = function() {
  if (knitr::is_latex_output())
    "latex" else "pipe"
})

Table_fun <- function(x){

table <- cbind(summary(x)$tTable, confint(x))

knitr::kable(table, caption = "PGLS summary")

}


##Load Packages
library(ape)
library(phytools)
library(nlme)
#library(tidyverse)
library(ggplot2)
library(dplyr)
library(geiger)
#library(caper)
#library(xlsx)
library(here)
library(readxl)
library(StanHeaders)
library(brms)
#library(kable)
library(rstan)
library(gdata)
library(bayesplot)

#Run this and skip to line 348
load(here('./Data/Output/CurrentDataState.RData'))

```

# Model Comparisons

## Model 1 - CFAR ~ GSH

1. brms model
```
Model_plain <- brm(Log10CFAR ~ Log10MeanGSH_centered,
                    data = GSH_df_pgls,
                    family = gaussian(),
                    prior = Plain_prior
                    )
```

```{r }
knitr::kable(fixef(Model_plain, summary = T))


```


```{r echo=FALSE}

plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(Model_plain, summary = F)[i,1], fixef(Model_plain, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

 abline(fixef(Model_plain)[1,1], fixef(Model_plain)[2,1], col = 'blue', lw = 2)
```


2. STAN model

Data considered
```
data {
  int <lower=1> N;
  vector[N] x;
  vector[N] y;
}
```
The parameters accepted by the model
```
parameters {
  real alpha;
  real beta;
  real<lower=0> sigma;
}
```
Model form:
```
model {
  
  sigma ~ student_t(3, 0, 10);
  
  y ~ normal(alpha + x * beta , sigma);
}
```
```{r echo=FALSE}
fit1_summary <- summary(fit1, pars = c("alpha", "beta","sigma"), probs = c(0.025, 0.975))$summary
```

```{r}
knitr::kable(fit1_summary, caption = 'STAN model summary')
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(posterior$alpha[i], posterior$beta[i], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

abline(fixef(Model_plain)[1,1], fixef(Model_plain)[2,1], col = 6, lw = 2)

abline(mean(posterior$alpha), mean(posterior$beta), col = 'red', lw = 1)
```
\newpage

## Model 2 - CFAR ~ GSH * Max Size

1. brms model
```
Model_size <- brm(Log10CFAR ~ Log10MeanGSH_centered * Log10MaxSize_centered,
                    data = GSH_df_pgls,
                    family = gaussian(),
                    prior = Size_prior
                    )
  ```                  
```{r}
fixef(Model_size, summary = T)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(Model_size, summary = F)[i,1], fixef(Model_size, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

 abline(fixef(Model_size)[1,1], fixef(Model_size)[2,1], col = 'blue', lw = 2)
```


2. STAN model

Data considered

```

data {
  int <lower=0> N; // number of data points
  int <lower=0> K; // number of predictors
  matrix[N,K] x; // predictor matrix
  vector[N] y; // CFAR
}
```

The parameters accepted by the model. 
```
parameters {
  real alpha;
  vector[K] beta;
  real<lower=0> sigma;
}
```

The model to be estimated. We model the output 'y' to be normally distributed with mean 'mu' and standard deviation 'sigma'.

```
model {

  sigma ~ student_t(3, 0, 10);

  y ~ normal(alpha + x * beta , sigma);
}
```

```{r echo=FALSE}
fit2_summary <- summary(fit2, pars = c("beta[1]", "beta[2]","beta[3]","beta[4]","sigma"), probs = c(0.025, 0.975))$summary

```

```{r}
knitr::kable(fit2_summary, caption = 'STAN model summary')
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20) 

for (i in 1:500) {
 abline(posterior2[i,1], posterior2[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
} 

 abline(fixef(Model_size)[1,1], fixef(Model_size)[2,1], col = 'blue', lw = 2)


abline(mean(posterior2[,1]), mean(posterior2[,2]), col = 'red', lw = 2)

```
\newpage

## Model 3 - CFAR ~ GSH + Max Size (No interaction)

1. brms model

```
Model_size_2 <- brm(Log10CFAR ~ Log10MeanGSH_centered + Log10MaxSize_centered,
                    data = GSH_df_pgls,
                    family = gaussian(),
                    prior = Size_prior_2)
```
```{r}
summary(Model_size_2)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(Model_size_2, summary = F)[i,1], fixef(Model_size_2, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

 abline(fixef(Model_size_2)[1,1], fixef(Model_size_2)[2,1], col = 'blue', lw = 2)
```

2. STAN model


Data considered

```

data {
  int <lower=0> N; // number of data points
  int <lower=0> K; // number of predictors
  matrix[N,K] x; // predictor matrix
  vector[N] y; // CFAR
}
```

The parameters accepted by the model. 

```
parameters {
  real alpha;
  vector[K] beta;
  real<lower=0> sigma;
}
```

The model to be estimated. We model the output 'y' to be normally distributed with mean 'mu' and standard deviation 'sigma'.

```
model {

  sigma ~ student_t(3, 0, 10);

  y ~ normal(alpha + x * beta , sigma);
}
```

```{r}
fit3_summary <- summary(fit3, pars = c("beta[1]", "beta[2]","sigma"), probs = c(0.025, 0.975))$summary
```

```{r}
knitr::kable(fit3_summary, caption = 'STAN model summary')
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20) 

for (i in 1:500) {
 abline(posterior3$alpha[i], posterior3[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
} 


 abline(fixef(Model_size_2)[1,1], fixef(Model_size_2)[2,1], col = 'blue', lw = 2)

abline(mean(posterior3$alpha), mean(posterior3[,2]), col = 'red', lw = 2)

```
\newpage

## Model 4 - CFAR ~ GSH + PrimaryHabitat (No interaction)

1. brms model
```
habitat_model <- brm(Log10CFAR ~ Log10MeanGSH_centered + PrimaryHabitat,
                    data = GSH_df_pgls,
                    family = gaussian(),
                    prior = habitat_prior,
                    cores = 2)
```

```{r}
summary(habitat_model)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(habitat_model, summary = F)[i,1], fixef(habitat_model, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

 abline(fixef(habitat_model)[1,1], fixef(habitat_model)[2,1], col = 'blue', lw = 2)
```


2. STAN model

Data considered

```

data {
  int <lower=0> N; // number of data points
  int <lower=0> K; // number of predictors
  matrix[N,K] x; // predictor matrix
  vector[N] y; // CFAR
}
```

The parameters accepted by the model. 

```
parameters {
  real alpha;
  vector[K] beta;
  real<lower=0> sigma;
}
```

The model to be estimated. We model the output 'y' to be normally distributed with mean 'mu' and standard deviation 'sigma'.

```
model {

  sigma ~ student_t(3, 0, 10);

  y ~ normal(alpha + x * beta , sigma);
}
```

```{r}
fit6_summary <- summary(fit6, pars = c("beta[1]", "beta[2]","beta[3]","beta[4]", "sigma"), probs = c(0.05, 0.95))$summary
print(fit6_summary)

```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20) 

for (i in 1:500) {
 abline(posterior6[i,1], posterior6[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
} 


 abline(fixef(habitat_model)[1,1], fixef(habitat_model)[2,1], col = 'blue', lw = 2)

abline(mean(posterior6[,1]), mean(posterior6[,2]), col = 'red', lw = 2)

```

\newpage

## Model 5 - CFAR ~ GSH * PrimaryHabitat
1. brms model
```
habitat_model_2 <- brm(Log10CFAR ~ Log10MeanGSH_centered * PrimaryHabitat,
                    data = GSH_df_pgls,
                    family = gaussian(),
                    prior = habitat_prior2,
                    cores = 2)
```
```{r}
summary(habitat_model_2)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(habitat_model_2, summary = F)[i,1], fixef(habitat_model_2, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

 abline(fixef(habitat_model_2)[1,1], fixef(habitat_model_2)[2,1], col = 'blue', lw = 2)
```

2. STAN model

Data considered

```

data {
  int <lower=0> N; // number of data points
  int <lower=0> K; // number of predictors
  matrix[N,K] x; // predictor matrix
  vector[N] y; // CFAR
}
```

The parameters accepted by the model. 

```
parameters {
  real alpha;
  vector[K] beta;
  real<lower=0> sigma;
}
```

The model to be estimated. We model the output 'y' to be normally distributed with mean 'mu' and standard deviation 'sigma'.

```
model {

  sigma ~ student_t(3, 0, 10);

  y ~ normal(alpha + x * beta , sigma);
}
```

```{r}
fit7_summary <- summary(fit7, pars = c("beta[1]", "beta[2]","beta[3]","beta[4]", "sigma"), probs = c(0.05, 0.95))$summary
print(fit7_summary)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20) 

for (i in 1:500) {
 abline(posterior7[i,1], posterior7[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
} 


 abline(fixef(habitat_model_2)[1,1], fixef(habitat_model_2)[2,1], col = 'blue', lw = 2)

abline(mean(posterior7[,1]), mean(posterior7[,2]), col = 'red', lw = 2)

```

\newpage

## Model 6 - CFAR ~ GSH + Phylogeny

1. PGLS model
```
pglsMod1 <- gls(Log10CFAR ~ Log10MeanGSH_centered, correlation = corPagel(phy = SampleTree, value = 0.5, fixed = F, form = ~Binomial), data = GSH_df_pgls, method = "ML")
```

```{r echo=FALSE}

Table_fun(pglsMod1)

```

```{r echo=FALSE}
plot(Log10CFAR ~ Log10MeanGSH_centered, data = GSH_df_pgls, pch = 20)
abline(a = coef(pglsMod1)[1], b = coef(pglsMod1)[2], col = 6, lw = 2)
```

2. brms model
```
Model_simple <- brm(Log10CFAR ~ Log10MeanGSH_centered + (1|gr(Binomial, cov = A)),
                    data = GSH_df_pgls,
                    family = gaussian(),
                    data2 = list(A = A),
                    prior = Simple_prior,
                    cores = 2)
```
                    
```{r}
summary(Model_simple)
```


```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(Model_simple, summary = F)[i,1], fixef(Model_simple, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

abline(a = coef(pglsMod1)[1], b = coef(pglsMod1)[2], col = 6, lw = 2)

 abline(fixef(Model_simple)[1,1], fixef(Model_simple)[2,1], col = 'blue', lw = 2)
```

3. STAN model


Data considered

```
data {
  int <lower=0> N; // number of data points
  int <lower=0> K; // number of predictors 
  matrix[N,K] x; // predictor matrix
  vector[N] y; // outcome (CFAR)
  matrix[N, N] d_mat; // sigma matrix
  matrix[N, N] A; // vcov matrix
      }
```

The parameters accepted by the model. 

```
 parameters {
        real alpha;
        vector[K] beta; // coefficients
        real<lower=0> sigma; // error
        real<lower=0,upper=1> lambda; // phylogenetic signal
      }
      
      
      transformed parameters {
        
        matrix[N, N] sigma_mat;
        matrix[N, N] sigma_total;
        
        vector[N] mu_y;
        

        sigma_mat = (1-lambda)*d_mat + lambda*A;
        sigma_total = sigma*sigma_mat;
        
        

      }
```

The model to be estimated. We model the output 'y' to be normally distributed with mean 'mu' and standard deviation 'sigma'.

```
model {
  
  beta ~ student_t(3, 0, 10);
  lambda ~ uniform(0,1);
  sigma ~ student_t(3, 0, 2.5);
  
  y ~ multi_normal(alpha + x * beta, sigma_total);
}
```

```{r}
fit4
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20) 

for (i in 1:200) {
 abline(posterior4$alpha[i], posterior4$beta[i], col = adjustcolor("gray", alpha = 0.15), lty = 1)
} 


abline(a = coef(pglsMod1)[1], b = coef(pglsMod1)[2], col = 6, lw = 2)

 abline(fixef(Model_simple)[1,1], fixef(Model_simple)[2,1], col = 'blue', lw = 2)

abline(mean(posterior4$alpha), mean(posterior4$beta), col = 'red', lw = 2)

```

\newpage

## Model 7 - CFAR ~ GSH * Max Size + Phylogeny

1. PGLS model

```
pglsMod2 <- gls(Log10CFAR ~ Log10MeanGSH_centered * Log10MaxSize_centered, correlation = corPagel(phy = SampleTree, value = 0.5, fixed = F, form = ~Binomial), data = GSH_df_pgls, method = "ML")
```


```{r}
Table_fun(pglsMod2)
```

```{r echo=FALSE}
plot(Log10CFAR ~ Log10MeanGSH_centered, data = GSH_df_pgls, pch = 20)

abline(a = coef(pglsMod2)[1], b = coef(pglsMod2)[2], col = 6, lw = 2)
```


2. brms model
```
Model_BS <- brm(Log10CFAR ~ Log10MeanGSH_centered * Log10MaxSize_centered + (1|gr(Binomial, cov = A)),
                    data = GSH_df_pgls,
                    family = gaussian(),
                    data2 = list(A = A),
                    prior = BS_prior,
                sample_prior = TRUE, chains = 4, cores = 2)
```

```{r}
summary(Model_BS)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(Model_BS, summary = F)[i,1], fixef(Model_BS, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

abline(a = coef(pglsMod2)[1], b = coef(pglsMod2)[2], col = 6, lw = 2)

 abline(fixef(Model_BS)[1,1], fixef(Model_BS)[2,1], col = 'blue', lw = 2)
```

3. STAN model

Data considered

```
data {
  int <lower=0> N; // number of data points
  int <lower=0> K; // number of predictors 
  matrix[N,K] x; // predictor matrix
  vector[N] y; // outcome (CFAR)
  matrix[N, N] d_mat; // sigma matrix
  matrix[N, N] A; // vcov matrix
      }
```

The parameters accepted by the model. 

```
 parameters {
        real alpha;
        vector[K] beta; // coefficients
        real<lower=0> sigma; // error
        real<lower=0,upper=1> lambda; // phylogenetic signal
      }
      
      
      transformed parameters {
        
        matrix[N, N] sigma_mat;
        matrix[N, N] sigma_total;
        
        vector[N] mu_y;
        

        sigma_mat = (1-lambda)*d_mat + lambda*A;
        sigma_total = sigma*sigma_mat;
        
        

      }
```

The model to be estimated. We model the output 'y' to be normally distributed with mean 'mu' and standard deviation 'sigma'.

```
model {
  
  beta ~ student_t(3, 0, 10);
  lambda ~ uniform(0,1);
  sigma ~ student_t(3, 0, 2.5);
  
  y ~ multi_normal(alpha + x * beta, sigma_total);
}
```

```{r}
fit5
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20) 

for (i in 1:200) {
 abline(posterior5$alpha[i], posterior5[i,2], col = adjustcolor("gray", alpha = 0.15), lty = 1)
} 


abline(a = coef(pglsMod2)[1], b = coef(pglsMod2)[2], col = 6, lw = 2)

 abline(fixef(Model_BS)[1,1], fixef(Model_BS)[2,1], col = 'blue', lw = 2)

abline(mean(posterior5$alpha), mean(posterior5[,2]), col = 'red', lw = 2)

```

\newpage

## Model 8 - CFAR ~ GSH + Max Size + Phylogeny

1. PGLS model

```
pglsMod3 <- gls(Log10CFAR ~ Log10MeanGSH_centered + Log10MaxSize_centered, correlation = corPagel(phy = SampleTree, value = 0.5, fixed = F, form = ~Binomial), data = GSH_df_pgls, method = "ML")
```

```{r}
Table_fun(pglsMod3)
```

```{r echo=FALSE}
plot(Log10CFAR ~ Log10MeanGSH_centered, data = GSH_df_pgls, pch = 20)

abline(a = coef(pglsMod3)[1], b = coef(pglsMod3)[2], col = 6, lw = 2)
```

2. brms model
```
Model_BS <- brm(Log10CFAR ~ Log10MeanGSH_centered + Log10MaxSize_centered + (1|gr(Binomial, cov = A)),
                    data = GSH_df_pgls,
                    family = gaussian(),
                    data2 = list(A = A),
                    prior = BS_prior,
                sample_prior = TRUE, chains = 4, cores = 2)
```

```{r}
summary(Model_BS2)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(Model_BS, summary = F)[i,1], fixef(Model_BS, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

abline(a = coef(pglsMod3)[1], b = coef(pglsMod3)[2], col = 6, lw = 2)

 abline(fixef(Model_BS2)[1,1], fixef(Model_BS2)[2,1], col = 'blue', lw = 2)
```

3. STAN model


Data considered

```
data {
  int <lower=0> N; // number of data points
  int <lower=0> K; // number of predictors 
  matrix[N,K] x; // predictor matrix
  vector[N] y; // outcome (CFAR)
  matrix[N, N] d_mat; // sigma matrix
  matrix[N, N] A; // vcov matrix
      }
```

The parameters accepted by the model. 

```
 parameters {
        real alpha;
        vector[K] beta; // coefficients
        real<lower=0> sigma; // error
        real<lower=0,upper=1> lambda; // phylogenetic signal
      }
      
      
      transformed parameters {
        
        matrix[N, N] sigma_mat;
        matrix[N, N] sigma_total;
        
        vector[N] mu_y;
        

        sigma_mat = (1-lambda)*d_mat + lambda*A;
        sigma_total = sigma*sigma_mat;
        
        

      }
```

The model to be estimated. We model the output 'y' to be normally distributed with mean 'mu' and standard deviation 'sigma'.

```
model {
  
  beta ~ student_t(3, 0, 10);
  lambda ~ uniform(0,1);
  sigma ~ student_t(3, 0, 2.5);
  
  y ~ multi_normal(alpha + x * beta, sigma_total);
}
```

```{r}
fit3
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20) 

for (i in 1:200) {
 abline(posterior3[i,1], posterior3[i,2], col = adjustcolor("gray", alpha = 0.15), lty = 1)
} 


abline(a = coef(pglsMod3)[1], b = coef(pglsMod3)[2], col = 6, lw = 2)

 abline(fixef(Model_BS2)[1,1], fixef(Model_BS2)[2,1], col = 'blue', lw = 2)

abline(mean(posterior3$alpha), mean(posterior3[,2]), col = 'red', lw = 2)

```
\newpage

## Model 9 - CFAR ~ GSH + PrimaryHabitat + Phylogeny
1. PGLS model
```
pglsMod5 <- gls(Log10CFAR ~ Log10MeanGSH_centered + PrimaryHabitat, 
                correlation = corPagel(phy = SampleTree, value = 0.5, fixed = F, form = ~Binomial), 
                data = GSH_df_pgls, method = "ML")
```

```{r}
summary(pglsMod5)
```


```{r echo=FALSE}
plot(Log10CFAR ~ Log10MeanGSH_centered, data = GSH_df_pgls, pch = 20)

abline(a = coef(pglsMod5)[1], b = coef(pglsMod5)[2], col = 6, lw = 2)
```
2. brms model
```
HabitatPhylo <- brm(Log10CFAR ~ Log10MeanGSH_centered + Log10MaxSize_centered + (1|gr(Binomial, cov = A)),
                    data = GSH_df_pgls,
                    family = gaussian(),
                    data2 = list(A = A),
                    prior = BS_prior2,
                sample_prior = TRUE, chains = 4, cores = 2)
```

```{r}
summary(HabitatPhylo)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(HabitatPhylo, summary = F)[i,1], fixef(HabitatPhylo, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

abline(a = coef(pglsMod5)[1], b = coef(pglsMod5)[2], col = 6, lw = 2)

 abline(fixef(HabitatPhylo)[1,1], fixef(HabitatPhylo)[2,1], col = 'blue', lw = 2)
```

3. STAN Model

\newpage

## Model 10 - CFAR ~ GSH * PrimaryHabitat + Phylogeny
1. PGLS model

```
pglsMod6 <- gls(Log10CFAR ~ Log10MeanGSH_centered * PrimaryHabitat, 
                correlation = corPagel(phy = SampleTree, value = 0.5, fixed = F, form = ~Binomial),
                data = GSH_df_pgls, method = "ML")

```

```{r echo=FALSE}
Table_fun(pglsMod6)
```

```{r echo=FALSE}
plot(Log10CFAR ~ Log10MeanGSH_centered, data = GSH_df_pgls, pch = 20)

abline(a = coef(pglsMod6)[1], b = coef(pglsMod6)[2], col = 6, lw = 2)
```

2. BRMS Model
```
HabitatPhylo2 <- brm(Log10CFAR ~ Log10MeanGSH_centered * PrimaryHabitat + (1|gr(Binomial, cov = A)),
                    data = GSH_df_pgls,
                    family = gaussian(),
                    data2 = list(A = A),
                    prior = HabitatPhylo_prior2,
                sample_prior = TRUE, chains = 4, cores = 4)
          
```


```{r}
summary(HabitatPhylo2)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(HabitatPhylo2, summary = F)[i,1], fixef(HabitatPhylo2, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

abline(a = coef(pglsMod6)[1], b = coef(pglsMod6)[2], col = 6, lw = 2)

 abline(fixef(HabitatPhylo2)[1,1], fixef(HabitatPhylo2)[2,1], col = 'blue', lw = 2)
```

3. STAN Model

\newpage
## Model 11 - CFAR ~ GSH * MaxSize + PrimaryHabitat + Phylogeny
1. PGLS model

```
pglsMod8 <- gls(Log10CFAR ~ Log10MeanGSH_centered * Log10MaxSize_centered + PrimaryHabitat, 
                correlation = corPagel(phy = SampleTree, value = 0.5, fixed = F, form = ~Binomial),
                data = GSH_df_pgls, method = "ML")
```

```{r echo=FALSE}
Table_fun(pglsMod8)
```

```{r echo=FALSE}
plot(Log10CFAR ~ Log10MeanGSH_centered, data = GSH_df_pgls, pch = 20)

abline(a = coef(pglsMod8)[1], b = coef(pglsMod8)[2], col = 6, lw = 2)
```


2. BRMS Model
```
SizeHabitatModel <- brm(Log10CFAR ~ Log10MeanGSH_centered * Log10MaxSize_centered + PrimaryHabitat + (1|gr(Binomial, cov = A)),
                    data = GSH_df_pgls,
                    family = gaussian(),
                    data2 = list(A = A),
                    prior = SizeHabitatMod_prior,
                sample_prior = TRUE, chains = 4, cores = 4)
```

```{r}
summary(SizeHabitatModel)
```

```{r echo=FALSE}
plot(GSH_df_pgls$Log10CFAR ~ GSH_df_pgls$Log10MeanGSH_centered, pch = 20)

for (i in 1:500) {
 abline(fixef(SizeHabitatModel, summary = F)[i,1], fixef(SizeHabitatModel, summary = F)[i,2], col = adjustcolor("gray", alpha = 0.05), lty = 1)
}

abline(a = coef(pglsMod8)[1], b = coef(pglsMod8)[2], col = 6, lw = 2)

 abline(fixef(SizeHabitatModel)[1,1], fixef(SizeHabitatModel)[2,1], col = 'blue', lw = 2)
```

3. STAN Model
